### 2021-09-06 presentation/presentation.tex
mpc graphic

\begin{frame}{Context}
  \begin{figure}
    \includegraphics<1>[width=.6\textwidth]{the_city_nothing.pdf}%
    \includegraphics<2>[width=.6\textwidth]{the_city_houses.pdf}%
    \includegraphics<3>[width=.6\textwidth]{the_city_buildings.pdf}%
    \includegraphics<4>[width=.6\textwidth]{the_city_cars.pdf}%
  \end{figure}
  \onslide<5->{
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{the_city_cars.pdf}%
  \end{minipage}
  \begin{minipage}{.5\textwidth}
    \begin{itemize}
      \item<6> Geographically distributed
      \item<7> Coupled by constraints (energy)
      \item<8> Optimization objectives
            \begin{itemize}
              \item Energy
              \item User satisfaction
              \item \dots
            \end{itemize}
      \item<9> Solution $\to$ Model Predictive Control
    \end{itemize}
  \end{minipage}
  }
\end{frame}

\begin{frame}{Model Predictive Control}
  Find control input sequence that optimizes an objective function

\begin{equation*}
\begin{matrix}
\underset{\vec{u}(k:k+N_{p}-1|k)}{\mathrm{minimize}}&\resizebox{0.35\textwidth}{!}{$ \overbrace{\sum_{j=1}^{N_{p}}\|\vec{v}(k+j|k)\|^{2}_{Q}+\|\vec{u}(k+j-1|k)\|^{2}_{R}}^{\textstyle J_{G}(k)}$}\\
\mathrm{subject~ to}&
\left.\begin{matrix}
    \vec{x}(k+1)=f(\vec{x}(k),\vec{u}(k)) \\
    g_{i}(\vec{x}(k),\vec{u}(k))=0\\
    h_{k}(\vec{x}(k),\vec{u}(k))\leq0\\
\end{matrix}
\right\}
\begin{aligned}
  &\forall i\in\{1,\dots,N_{p}\}\\
  &\forall j\in\{1,\dots,N_{p}\}\\
  &\forall k\in\{1,\dots,N_{p}\}
\end{aligned}
\end{matrix}
\end{equation*}
  Using
\end{frame}

>>>>

\begin{frame}{Context}
  \begin{figure}
    \includegraphics<1>[width=.6\textwidth]{the_city_nothing.pdf}%
    \includegraphics<2>[width=.6\textwidth]{the_city_houses.pdf}%
    \includegraphics<3>[width=.6\textwidth]{the_city_buildings.pdf}%
    \includegraphics<4>[width=.6\textwidth]{the_city_cars.pdf}%
  \end{figure}
  \only<5->{
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{the_city_cars.pdf}%
  \end{minipage}
  \begin{minipage}{.5\textwidth}
    \begin{itemize}
      \item<6> Geographically distributed
      \item<7> Coupled by constraints (energy)
      \item<8> Optimization objectives
            \begin{itemize}
              \item Energy
              \item User satisfaction
              \item \dots
            \end{itemize}
      \item<9> Solution $\to$ Model Predictive Control
    \end{itemize}
  \end{minipage}
  }
\end{frame}

\begin{frame}{Model Predictive Control}
  Objective: Find control input sequence that optimizes an objective function
  \only<1-5>{\begin{equation*}
    \begin{matrix}
      \underset{\vec{u}(k:k+\alert<3>{N_{p}}-1|k)}{\mathrm{optimize}}&\alert<2>{J(\vec{x}(k),\vec{u}(k))}\\
      \mathrm{subject~ to}&
      \left.
        \begin{matrix}
          \alert<4>{\vec{x}(\xi+1)=f(\vec{x}(\xi),\vec{u}(\xi))}\\
          \alert<5>{g_{i}(\vec{x}(\xi),\vec{u}(\xi))\leq0}\\
          \alert<5>{h_{j}(\vec{x}(\xi),\vec{u}(\xi))=0}\\
        \end{matrix}
      \right\}
      \begin{aligned}
        &\forall \xi\in\{1,\dots,\alert<3>{N_{p}}\}\\
        &\forall i\in\{1,\dots,m\}\\
        &\forall j\in\{1,\dots,p\}
      \end{aligned}
    \end{matrix}
  \end{equation*}}%
\only<6->{
  \begin{equation*}
    \begin{matrix}
      \underset{\vec{u}(k:k+N_{p}-1|k)}{\mathrm{minimize}}&  \sum_{j=1}^{N_{p}}\|\vec{v}(k+j|k)\|^{2}_{Q}+\|\vec{u}(k+j-1|k)\|^{2}_{R}\\
      \mathrm{subject~ to}&
      \left.
        \begin{matrix}
          \vec{x}(\xi+1)=f(\vec{x}(\xi),\vec{u}(\xi)) \\
          g_{i}(\vec{x}(\xi),\vec{u}(\xi))\leq0\\
          h_{j}(\vec{x}(\xi),\vec{u}(\xi))=0\\
        \end{matrix}
      \right\}
      \begin{aligned}
        &\forall \xi\in\{1,\dots,N_{p}\}\\
        &\forall i\in\{1,\dots,m\}\\
        &\forall j\in\{1,\dots,p\}
      \end{aligned}
    \end{matrix}
  \end{equation*}
  }%
\end{frame}

\begin{frame}{Model Predictive Control}
  Find sequence, \pause apply first control, \pause rinse repeat \pause $\to$ Receding Horizon

  \begin{figure}
    \centering
    \foreach \i in {1,...,10}{\includegraphics<\i>[width=.5\textwidth]{mpc\i.pdf}%
    }
  \end{figure}
\end{frame}

\begin{frame}
  \begin{itemize}
    \item Problem: Complexity depends on $N_{p},m,p$ and sizes of $\vec{x}$ and $\vec{u}$
    \item Solution: Divide and Conquer
  \end{itemize}
\end{frame}
